Refinements for open automata

### 2023-03-08 2021-Refinement/paper/refinementarticleV2.tex
case 2 -- Congruence

For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$ and $g_{13x}  \Leftrightarrow g^2_1$ and the actions of $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} = = \alpha^2_1$ and the actions of the holes in $J_{13}$ coincide by the composition.

The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.

By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.

>>>>

For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$, $g_{13x}  \Leftrightarrow g^2_1$, $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} =  \alpha^2_1$.  Furthermore, we have the actions of the holes in $J_{13}$ coincide by the composition, $\beta_{13j}$ and $\beta_{23xj}$  are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.

\TODO{D'apres l'hypothese de depart, la formule (*) nous obtenons une formule sous cette forme: $R\mpar{s_2, s_3} \wedge g_2 \implies R\mpar{s'_2, s'_{3x}}$  l'idee est de faire disparaitre g2. On a la formule suivante:}

According to the relation between $A_2$ and $A_3$ open automata,  for all $\mpar{s_2, s_{3}} \in S_2\times S_3$  we have:
\begin{multline*}
 V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \wedge \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} )\implies \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}  )
\end{multline*}

\TODO{La conjonction des deux donne $False \implies R\mpar{s'_2, s'_{3x}}$ qui true???}

%By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
